Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed

### 2012-11-29 paper.tex
Intro skeleton
Switching machines
paradigm 1 outline

\section{Introduction}
Hello World!

\section{Paradigm 1 - Discrete Formulation}
Hello World!

>>>>

\section{Introduction}
-- Explanation of pursuit-evasion problem in general.
-- The two various methods for analyzing the problem
-- a solution for blending the two solutions together

\section{Paradigm 1 - Discrete Formulation}
-- explanation of the paradigm
-- mathematical definitions
-- planar graphs need max three pursuers
